### 2014-05-08 R/Neutral_simul.Rmd
Add simulations with more ReplacementR values

@@

system(paste(neuBin,"sim.par","fishE.inp"),wait=F)

@@

Let's try simulations with different parameters using pomac and at Time=100

@@

```{r testKS_pomac467}

@@

mks <-adply(combo,2, function(x) {
      p1 <- parms[x[1],]
      p2 <- parms[x[2],]
      d1 <- merge(den1,p1)
      d2 <- merge(den1,p2)
      ks <- ks.test(d1$value,d2$value)
      out <-data.frame(t(paste(p1,p2,sep="-")),p.value=ks$p.value)
      names(out)[1:length(names(p1))]<-names(p1)
      return(out)      
      })

@@

# wich are not different
format(mks[mks$p.adjust>0.05,c(2:5,7)],digits=4)

#rm(d1,d2,p1,p2,out,ks,x)

# USING THE SAME adply technique a data.frame for ggplot could be generated!!!!!

@@

The most important not-different are the ones that correspond to neutral vs non-neutral
thus we will try to differentiate them using Dq

>>>>

s_wait <- F # variable to make R wait until simulations ends or not

@@

system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

@@

Let try simulations with different parameters using pomac and at Time=100

@@

```{r testKS_pomac467}
# Read simulation output and change from wide to long format NO TIME
#
meltDensityOut_NT <- function(fname,num_sp){
  den <- read.delim(fname)
  names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")

  # from 7 to 473 there are species densities
  # Put simpler names to variables to identify species
  names(den)[7:(6+num_sp)]<-as.character(1:num_sp)

}

@@

require(plyr)
mks <-adply(combo,2, function(x) {
      p1 <- parms[x[1],]
      p2 <- parms[x[2],]
      d1 <- merge(den1,p1)
      d2 <- merge(den1,p2)
      ks <- ks.test(d1$value,d2$value)
      out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
      ln <-length(names(p1))*3
      names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
      return(out)      
      })

#p1 <- parms[1,]
#p2 <- parms[9,]
#d1 <- merge(den1,p1)
#d2 <- merge(den1,p2)
#ks <- ks.test(d1$value,d2$value)
#out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
#ln <-length(names(p1))*3
#names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
#rm(d1,d2,p1,p2,out,ks,ln)

@@

# wich are not different

format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)
format(mks[mks$p.adjust>0.1,c(10:13,14:15)],digits=4)

format(mks[mks$p.value>0.01,c(10:13,14:15)],digits=4)

# Graph on pair with different mechanisms but not different SAD
#
# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
# den1: full data in long format
#
mergePairSAD <- function(eks, den1){
# eks <- mks[61,]

  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
  den2 <- den2[den2$value>0,]
  den2$parms <-paste(eks[,2:5],collapse="_")
  den2$Rank <- nrow(den2) - rank(den2$value) +1

  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
  den3 <- den3[den3$value>0,]
  den3$parms <-paste(eks[,6:9],collapse="_")
  den3$Rank <- nrow(den3) - rank(den3$value) +1
  den2 <- rbind(den2,den3)

  }
# SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!

#den2 <- ddply(den1,.(Time), function(x) { 
  #tmp <- x[x$value>0,]
#  tmp <- x[order(x$value),]
#  tmp$Ord <- nrow(x):1
#  data.frame(tmp)
#  })

format(mks[mks$p.value<0.05 & mks$p.adjust>0.05,c(10:13,14:15)],digits=4)

debug(plotPairSAD)
psa <-mergePairSAD(mks[61,],den1)
# p.value = 
require(ggplot2)
g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line()
g

psa <- mergePairSAD(mks[105,],den1)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
g + geom_point()
```

In this case there are no semejant SAD for different mechanisms (neutral vs hierarchical) but some of adjusted p values lead to not reject differences when SADs seems different like mks[61,],105,107

Now I will simulate with a smaller Replacement = 0.01 / 0.1 and compare with Replacement=0

```{r simul_pomac467_R001,echo=F,message=F,warning=F}

# read par file with simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100

par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

# I will not delete old simulations
# system("rm Exp467*")

# I have to modify pomExp.lin to make different simulations
#undebug(genPomacParms)

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.01))

system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

# add more paremeter combinations 
genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.1,0.01))
system("cp pomExp.lin pomac.lin")
system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

########### TEST THIS FUNCTION
den4 <- meltDensityOut_NT("Exp467Density.txt",nrow(ff))

@@
